### 2015-10-19 paper.tex
initial import

\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{sectsty}

\renewcommand{\refname}{}

\setlength{\paperheight}{297mm}
\setlength{\paperwidth}{210mm}
\setlength{\voffset}{-12mm}
\setlength{\topmargin}{0mm}
\setlength{\headsep}{8mm}
\setlength{\headheight}{10mm}
\setlength{\textheight}{235mm}
\setlength{\hoffset}{-4mm}
\setlength{\textwidth}{166mm}
\setlength{\oddsidemargin}{0mm}
\setlength{\evensidemargin}{0mm}
\setlength{\marginparwidth}{0mm}
\setlength{\marginparpush}{0mm}
\setlength{\columnsep}{6mm}
\setlength{\parindent}{6mm}
\setlength{\parskip}{2mm}

%% insert eps pictures
%% use as \epsin{epsfile}{width_in_mm}{label}{caption}
\usepackage{epsfig}
\newcounter{figcounter}
\def\epsin #1#2#3#4{
\refstepcounter{figcounter} \label{#3}
\[
\mbox{
  \epsfxsize=#2mm
  \epsffile{#1.eps}
}
\]
%\vspace{0mm}
\begin{center}
  \parbox{7cm}{{\bf FIGURE \arabic{figcounter}:}\quad {\it #4 } } \\
\end{center}
}

%% insert table
%% use as \tabin{size_in_mm}{label}{caption}{table_data}
\newcounter{tabcounter}
\def\tabin #1#2#3#4{
\refstepcounter{tabcounter} \label{#2}
\[ \makebox[#1mm][c]{#4} \]
%\vspace{0mm}
\begin{center}
  \parbox{7cm}{{\bf TABLE \arabic{tabcounter}:}\quad {\it #3 } } \\
\end{center}
}

\title{\LARGE
Performance Evaluation of Xenomai 3
}

\author{\large
{\bf Ching-Chun (Jim) Huang }\\
Department of Computer Science and Information Engineering, \\
National Cheng Kung University, Taiwan\\
No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
\vspace{8mm}
jserv$@$ccns.ncku.edu.tw\\
{\bf Chan-Hsiang Lin}\\
Department of Electrical and Electronic Engineering, National Taiwan University\\
No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% E-MAIL (REQUIRED)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
??\\
}
\date{}

\begin{document}

\maketitle

\begin{abstract}
Xenomai 3 is the new architecture of the real-time framework running seamlessly side-by-side Linux as a dual-kernel system like Xenomai 2, or natively over mainline Linux kernels supplemented by the PREEMPT\_RT efforts to meet stricter response time requirements than standard kernel preemption would bring. In this presentation, we will evaluate the performances of Xenomai 3 running with both configurations and analyze the various benchmarks for ARM Cortex-A series. Xenomai 3 introduces some optimizations over RTOS API emulation, thread-to-thread communications, and significantly lower overhead with dual-kernel configurations. The comprehensive performance comparisons illustrate the major evolution of Xenomai 3 along with the revised Real-Time Driver Model (RTDM) which provides a unified interface over both PREEMPT\_RT and dual-kernel.

This paper would be a report on performance measurements among upstream Linux real-time enhancements and Xenomai official stable release (both version 2 and 3 series), and and the benchmarks show that the maximum response time to external interrupts of the dual kernel configurations for Xenomai 3 is almost twice as PPREEMPT\_RT, that more predictable handling on multiple incoming interrupts where Xenomai 3 supports both configurations interchangeably.
\end{abstract}

\vspace{10mm}

\begin{multicols}{2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION (REQUIRED)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Historically speaking, there are two typical approaches to modifying the standard Linux kernel into a real-time kernel. The first uses an extra small real-time executive \cite{rtai} or microkernel \cite{sel4} which runs the para-virtualized Linux kernel as a task. The small real-time executive takes control over the system for real-time processes and is responsible for scheduling real-time tasks, interrupt handling and scheduling Linux. With these changes it is possible to let a real-time task run on the CPU without the Linux kernel being able to interrupt the task. As the Linux kernel is run as a task it is preemptive at any time.

With the second approach, changes are made the Linux kernel in order to be real-time. This include changes as real-time
scheduling and adding preemption to the kernel.

In this section we briefly present the Xenomai real-time framework for Linux, and the Adaptive Domain Environment for Operating System (Adeos) layer, which allows Xenomai and Linux to run on the same hardware platform.

To provide an objective metric, we run processes on the test system, but measure their performance using an external measurement system which runs a C program on bare metal.

\subsection{Adeos layer}

\textit{Adeos} is a resource virtualization layer, allowing multiple entities called \textit{domains}, that can be seen as complete operating systems, to run  simultaneously on the same hardware platform.

Adeos domains can compete with each other for receiving system generated \textit{events}. Those events can be incoming external (or virtually generated) interruptions, Linux system calls invocations, or various kernel-code-related events like context switches. Adeos introduces the \textit{event pipeline}, which can be seen as a chain of domains of decreasing priority. The events are consequently propagated throughout the pipeline, distributed firstly to the utmost priority domain, then distributed to lower priority domains.

In the case of a Xenomai RTOS running with a Linux kernel, the Adeos pipeline and the organization of the domains is depicted in Figure "EventPipeline". In the pipeline,  we can see that Xenomai has the highest priority, so it can handle and manage first the events before passing them to the Linux kernel. The events can also be blocked by the interrupt shield, preserving the real-time framework from latencies due to event management by the Linux kernel. Throughout this mechanism, Xenomai framework can provide real-time guarantees.

\subsection{Xenomai}

Xenomai provides a kernel-based Application Programming Interface (API) for real-time applications. A user-land API is also available, at the cost of longer latencies. Xenomai introduces the concept of \textit{skins}. Skins are source codes emulating proprietary APIs used for porting real-time applications from various RTOSs such as \textit{VxWorks}, \textit{pSOS}, etc. to Xenomai. When designing a Xenomai application from scratch, the \textit{native} Xenomai skin can be used.

All Xenomai skins rely on the \textit{nucleus}, the core of the RTOS, implementing all algorithms for real-time functionalities. Xenomai provides all standard services one can expect to find in a RTOS: task management, multiple scheduling algorithms, IPCs, etc.

\subsection{Time management in Xenomai}
We focused in this project on periodic real-time tasks that make extensive use of timers. A commonly used skeleton for those tasks in Xenomai as follows :

%\vspace{-0.5cm}
\begin{verbatim}
void myRealTimeTask(void *arg) {
  SetPeriodic(myself, period);
  while(1) {
    /* Do something */
    wait_period();
  }
}
\end{verbatim}
%\vspace{-0.5cm}

The \verb+SetPeriodic()+ function creates and starts a timer related to the calling task, with a period (in clock ticks) equals to the specified parameter. The global tick management function notifies the timer each time a clock tick occurs. When reaching wake up time, the timer executes a handler placing the task in the ready state.

The Gnublin mascot is the quadratic little man, adverting to the 
7x7 cm board dimensions (fig. \ref{fig-maennchen}).

\begin{figure}[H]
\begin{center}
\includegraphics[width=3cm]{img/gnublin-maennchen.jpg}
\caption{The Gnublin mascot.}
\label{fig-maennchen}
\end{center}
\end{figure}

\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{Multi-Row} &
\multicolumn{2}{c|}{Multi-Column} &
\multicolumn{2}{c|}{\multirow{2}{*}{Multi-Row and Col}} \\
\cline{2-3}
  & column-1 & column-2 & \multicolumn{2}{c|}{} \\
\hline
label-1 & label-2 & label-3 & label-4 & label-5 \\
\hline
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NEXT SECTION (OPTIONAL)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hardware System Structure}
Hardware structure of the recorder is shown as figure 1.The medium of data storage is several 10000RPM SCSI hard disks constituting RAID5.Hardware is based on 64-bit PCI bus, and Software is based on RTLinux and XFS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% FIGURES ARE HANDLED LIKE THIS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% the figure will be in file rt-tux.eps and will occupy 75mm on the page
\epsin{hsr}{80}{fig1:f1}{Hardware structure of Recorder}

\section{Conclusions}
The trait of real time in RTLinux is closely related to hardware, So we can take full advantage of PC. The testing on our recorder showed that the average of interrupt response time is 10us, and the max  is 15us. This performance can satisfy this real time requirement of recorder completely and guarantee data integrity. With the high-performance and  great capacity hard disk using, the capacity of the RAID would reach over 1000GB, moreover, collected data don't loss even if one hard disk is demaged.

We had done the test that  under the same hard platform, the recording speed has significantly enhanced in RTLinux than in Windows NT. RTLinux is free, open source, retractile, and transferable, so many OS can not bear comparison with it. RTLinux has been applied successful in our pre-demodulation Digital Recorder; moreover, it will be more widely used in the field of real-time control.

\bibliographystyle{plain}
\begin{thebibliography}{9}%use this if you have <=9 bib refs
	\bibitem {rtai}{\it https://www.rtai.org/}
	\bibitem {sel4}{\it http://ssrg.nicta.com.au/projects/seL4/}
\end{thebibliography}

\end{multicols}
\end{document}

### 2015-10-19 paper.tex
Add author (me) & add gitignore
Add Experiment paragraphs, graphs and tables

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-??\\
+r04943031$@$ntu.edu.tw
 }
@@
 
+\section{Experiment}
+
+\subsection{Purpose}
+1. Compare the performance of Xenomai with baseline Linux kernel and PREEMPT\_RT patched kernel
+2. Compare the performance of Xenomai-2 and Xenomai-3
+\subsection{Environment Setup}
+
+\subsubsection{Hardware}
+BeagleBone Black, an effective embedded platform with ARM Cortex-A8 processor, capable of running Linux and Xenomai (both 2 and 3), consisting of a single processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
+
+\subsubsection{Kernel}
+A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions).
+We selected Linux 3.18 for our experiment.
+In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.
+
+\subsubsection{Kernel configuration [ipipe]}
+Some of the kernel conﬁguration options may have an impact on real-time latencies.
+These options include Power Management, especially CPU frequency scaling, value of HZ, NUMA conﬁguration and so on.
+Additionally, most debug options (Kernel hacking section) lead to increased latencies.
+We disabled these config options before compilation.
+
+\subsubsection{Pre-experiment Settings}
+We tried to measure the latencies under 2 conditions - IDLE and CPU-STRESSED.
+In the IDLE experiment, in order to create such test environment, some redundant user processes were eliminated.
+While in the CPU-STRESSED condition, these process are also killed, and we used the 'stress' command to keep the CPU busy.
+The command to kill these processes are written in the test script.
+
+  The gravity values is the shortest time the platform needs to deliver an IRQ to a Xenomai interrupt handler,  a RTDM task running in kernel space, or a user-space task.
+It is used to differentiate timers on the target context they activate, among IRQ(handler), kernel and user threads, anticipating the next timer shot accordingly, so that such context is activated as close as possible to the ideal time.
+The gravity values can be set in the file `/proc/xenomai/latency` on Xenomai-2, `/proc/xenomai/clock/coreclk` on Xenomai-3 with root privilege.
+Furthermore, Xenomai-3 has an autotune function that runs a series of internal calibration tests for estimating the most appropriate gravity values for its real-time clock timer, retaining the final values.
+Because Xenomai-2 doesn't have an autotune function and it has only one gravity value for all the 
+coreclocks, we decided to manually tune all the coreclock values in both Xenomai-2 and Xenomai-3 to zero, so that we can later compare the results on the same basis.
+
+In our experiments, the kernel build were stored in different SD cards.
+The fact that different external storage devices have different access specs could affect the result.
+In order to eliminate the uncertainties, and for the sake of preventing the test process's pages being swapped into disk, we locked all the test process's pages inside memory.
+In cyclictest, this achieved by specifying the '-m' option in the command.
+On the other hand, latency is already executed in a memory locked condition.
+
+\subsection{Testing Process}
+
+\subsubsection{Scenario}
+The goal of the experiment is to evaluate the realtime performances of Mainline Linux, PREEMPT\_RT, 
+Xenomai-2 and Xenomai-3. Also, we want to find out whether the newly released Xenomai-3.0 has improved in realtime capability, compared to Xenomai-2.6.4, the latest stable version of Xenomai-2.
+\subsubsection{Tools}
+Cyclictest is a commonly-used latency benchmark.
+It is compatible with all the kernel setups we use (the recently Xenomai-3.0 release add cyclictest to its testsuite), therefore it's suitable for the purpose of measuring latencies for all setups.
+Latency is a test program for the Xenomai test suite.
+It can measure latencies under 3 modes - user task, kernel task, or timer IRQ.
+It launches the test procedure in one of the user-specified contexts.
+In the user mode, the measurement task is handled by the 'latency' function in the program, which periodically waits and fetches the current time when resuming.
+Latency is then measured by calculating the difference of the actual time elapsed with the predefined period.
+\subsubsection{Test Procedure}
+Each experiment was run on the same hardware. Each was run for 20 minutes to generate approximately 1,000,000 samples. Test scripts were written to facilitate the experiment process.
+\subsubsection{Test Load}
+As previously mentioned, we measure latencies under IDLE and CPU-STRESSED conditions. In the CPU-STRESSED condition, we called the "stress" process to exert pressure on the CPU.
+\subsection{Experiment Result}
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=8cm]{img/cyclictest_idle.jpg}
+\caption{Cyclictest with no stress.}
+\label{cyclictest-idle}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=8cm]{img/cyclictest_stress.jpg}
+\caption{Cyclictest with stress.}
+\label{cyclictest-tress}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=8cm]{img/latency_idle.jpg}
+\caption{Latency with no stress.}
+\label{latency-idle}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=8cm]{img/latency_stress.jpg}
+\caption{Latency with no stress.}
+\label{latency-stress}
+\end{center}
+\end{figure}
+
+\epsin{cyclic-idle}{80}{fig2:f2}{Cyclictest Idle}
+\epsin{cyclic-cpu}{80}{fig3:f3}{Cyclictest stressed}
+
+\resizebox{\columnwidth}{!}{%
+\begin{tabular}{|l|c|r|r|c|r|r|c|r|r|}
+\hline
+\multirow{2}{*}{} & \multicolumn{3}{c|}{user} & \multicolumn{3}{c|}{kernel} & \multicolumn{3}{c|}{timer-irq} \\ \cline{2-10} 
+ & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
+Xenomai 2 & \multicolumn{1}{r|}{8.541} & 9.458 & 34.583 & \multicolumn{1}{r|}{6.965} & 7.708 & 27.821 & \multicolumn{1}{r|}{2.129} & 2.654 & 11.343 \\ \hline
+Xenomai 3 & \multicolumn{1}{r|}{8.043} & 8.853 & 33.023 & \multicolumn{1}{r|}{5.567} & 6.479 & 25.577 & \multicolumn{1}{r|}{2.586} & 3.079 & 10.031 \\ \hline
+\end{tabular}
+}
+
+\begin{tabular}{|l|r|r|r|r|r|r|}
+\hline
+\multirow{2}{*}{} & \multicolumn{3}{c|}{idle} & \multicolumn{3}{c|}{cpu-stressed} \\ \cline{2-7} 
+ & \multicolumn{1}{l|}{min} & \multicolumn{1}{l|}{avg} & \multicolumn{1}{l|}{max} & \multicolumn{1}{l|}{min} & \multicolumn{1}{l|}{avg} & \multicolumn{1}{l|}{max} \\ \hline
+Mainline Linux & 39 & 43 & 1046 & 39 & 52 & 1097 \\ \hline
+Preempt-RT & 16 & 21 & 52 & 18 & 25 & 62 \\ \hline
+Xenomai 2 & 8 & 9 & 41 & 8 & 19 & 45 \\ \hline
+Xenomai 3 & 7 & 7 & 35 & 6 & 16 & 37 \\ \hline
+\end{tabular}
+
+From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 us) than on Xenomai-2(below 3 us).
+While this is not an occasional case(the same experiment was ran a couple times), we tried to look into the test code of latency to figure out the cause of this phenomenon.
+
+\subsection{Experiment Result Analysis}
+Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 us in idle situation, 18 us in stressed situation.
+And in the worse case, the latency is below 50 us.
+Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 us and can't guarantee a 50 us max latency (Actually in some cases the latency will exceed 100 us in stressed condition).
+As for mainline Linux, the max latency easily exceeds 1 ms.
+When comparing the performance of Xenomai-3 to Xenomai-2, we can see that the stats in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.
+
 \section{Conclusions}

### 2015-10-20 paper.tex
Fix : author section format issue
Fix : Kernel & Kernel configuration
Kernel : version 3.18 -> 3.14
configuration : NUMA not used, value of HZ?
    power management -> APM & Opportunistic sleep

@@
 No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% E-MAIL (REQUIRED)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-r04943031$@$ntu.edu.tw
+\vspace{8mm}
+r04943031$@$ntu.edu.tw\\
+{\bf Che-Kang Wu}\\
+Department of Computer Science and Information Engineering, \\
+National Cheng Kung University, Taiwan\\
+No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
+\vspace{8mm}
+an4006048$@$mail.ncku.edu.tw\\
 }
@@
 A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions).
-We selected Linux 3.18 for our experiment.
+We selected Linux 3.14 for our experiment.
 In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.
@@
 Some of the kernel conﬁguration options may have an impact on real-time latencies.
-These options include Power Management, especially CPU frequency scaling, value of HZ, NUMA conﬁguration and so on.
-Additionally, most debug options (Kernel hacking section) lead to increased latencies.
-We disabled these config options before compilation.
+These options include all options under CPU Power Management, APM support, and Opportunistic sleep.
+Additionally, most debug options in Kernel hacking section lead to increased latencies.
+Those options are disabled before compilation.
 

### 2015-10-20 paper.tex
Use thinner tables
For the paper width, it can only support about 5 columns without
resizing. And the table fonts are already small enougnh

@@
 
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{|l|c|r|r|c|r|r|c|r|r|}
+\begin{tabular}{|l|c|r|r|}
 \hline
-\multirow{2}{*}{} & \multicolumn{3}{c|}{user} & \multicolumn{3}{c|}{kernel} & \multicolumn{3}{c|}{timer-irq} \\ \cline{2-10} 
- & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
-Xenomai 2 & \multicolumn{1}{r|}{8.541} & 9.458 & 34.583 & \multicolumn{1}{r|}{6.965} & 7.708 & 27.821 & \multicolumn{1}{r|}{2.129} & 2.654 & 11.343 \\ \hline
-Xenomai 3 & \multicolumn{1}{r|}{8.043} & 8.853 & 33.023 & \multicolumn{1}{r|}{5.567} & 6.479 & 25.577 & \multicolumn{1}{r|}{2.586} & 3.079 & 10.031 \\ \hline
+\multirow{2}{*}{} & \multicolumn{3}{c|}{user} \\ \cline{2-4} 
+ & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
+Xenomai 2 & 8.541 & 9.458 & 34.583 \\ \hline
+Xenomai 3 & 8.043 & 8.853 & 33.023 \\ \hline
+& \multicolumn{3}{c|}{kernel}      \\ \hline
+Xenomai 2 & 6.965 & 7.708 & 27.821 \\ \hline
+Xenomai 3 & 5.567 & 6.479 & 25.577 \\ \hline
+& \multicolumn{3}{c|}{timer-irq}   \\ \hline
+Xenomai 2 & 2.129 & 2.654 & 11.343 \\ \hline
+Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
 \end{tabular}
-}
 
-\begin{tabular}{|l|r|r|r|r|r|r|}
+\begin{tabular}{|l|r|r|r|}
 \hline
-\multirow{2}{*}{} & \multicolumn{3}{c|}{idle} & \multicolumn{3}{c|}{cpu-stressed} \\ \cline{2-7} 
- & \multicolumn{1}{l|}{min} & \multicolumn{1}{l|}{avg} & \multicolumn{1}{l|}{max} & \multicolumn{1}{l|}{min} & \multicolumn{1}{l|}{avg} & \multicolumn{1}{l|}{max} \\ \hline
-Mainline Linux & 39 & 43 & 1046 & 39 & 52 & 1097 \\ \hline
-Preempt-RT & 16 & 21 & 52 & 18 & 25 & 62 \\ \hline
-Xenomai 2 & 8 & 9 & 41 & 8 & 19 & 45 \\ \hline
-Xenomai 3 & 7 & 7 & 35 & 6 & 16 & 37 \\ \hline
+\multirow{2}{*}{} & \multicolumn{3}{c|}{idle}  \\ \cline{2-4} 
+ & \multicolumn{1}{l|}{min} & \multicolumn{1}{l|}{avg} & \multicolumn{1}{l|}{max} \\ \hline
+Mainline Linux & 39 & 43 & 1046  \\ \hline
+Preempt-RT & 16 & 21 & 52 \\ \hline
+Xenomai 2 & 8 & 9 & 41 \\ \hline
+Xenomai 3 & 7 & 7 & 35 \\ \hline
+ & \multicolumn{3}{c|}{cpu-stressed} \\ \hline
+Mainline Linux & 39 & 52 & 1097 \\ \hline
+Preempt-RT & 18 & 25 & 62 \\ \hline
+Xenomai 2 & 8 & 19 & 45 \\ \hline
+Xenomai 3 & 6 & 16 & 37 \\ \hline
 \end{tabular}

### 2015-10-20 paper.tex
Remove unrelated (example?) section
If needed you can always check with gitk

@@
 
-The Gnublin mascot is the quadratic little man, adverting to the 
-7x7 cm board dimensions (fig. \ref{fig-maennchen}).
-
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width=3cm]{img/gnublin-maennchen.jpg}
-\caption{The Gnublin mascot.}
-\label{fig-maennchen}
-\end{center}
-\end{figure}
-
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\multirow{2}{*}{Multi-Row} &
-\multicolumn{2}{c|}{Multi-Column} &
-\multicolumn{2}{c|}{\multirow{2}{*}{Multi-Row and Col}} \\
-\cline{2-3}
-  & column-1 & column-2 & \multicolumn{2}{c|}{} \\
-\hline
-label-1 & label-2 & label-3 & label-4 & label-5 \\
-\hline
-\end{tabular}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% NEXT SECTION (OPTIONAL)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Hardware System Structure}
-Hardware structure of the recorder is shown as figure 1.The medium of data storage is several 10000RPM SCSI hard disks constituting RAID5.Hardware is based on 64-bit PCI bus, and Software is based on RTLinux and XFS.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% FIGURES ARE HANDLED LIKE THIS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% the figure will be in file rt-tux.eps and will occupy 75mm on the page
-\epsin{hsr}{80}{fig1:f1}{Hardware structure of Recorder}
-
 \section{Experiment}
@@
 A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions).
-We selected Linux 3.14 for our experiment.
+Linux 3.14 is selected for our experiment.
 In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.
 
-\subsubsection{Kernel configuration [ipipe]}
+\subsubsection{Kernel configuration }
 Some of the kernel conﬁguration options may have an impact on real-time latencies.

### 2015-10-20 paper.tex
Change the author introduction by putting jserv and Che-Kang  togother\

--- 2015-10-20 paper.tex
@@
 \author{\large
-{\bf Ching-Chun (Jim) Huang }\\
+{\bf Ching-Chun (Jim) Huang, Che-Kang Wu }\\
 Department of Computer Science and Information Engineering, \\
@@
 \vspace{8mm}
-jserv$@$ccns.ncku.edu.tw\\
+jserv$@$ccns.ncku.edu.tw, an4006048$@$mail.ncku.edu.tw\\
 {\bf Chan-Hsiang Lin}\\
@@
 r04943031$@$ntu.edu.tw\\
-{\bf Che-Kang Wu}\\
-Department of Computer Science and Information Engineering, \\
-National Cheng Kung University, Taiwan\\
-No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
-\vspace{8mm}
-an4006048$@$mail.ncku.edu.tw\\
 }
@@
 A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions).
-We selected Linux 3.14 for our experiment.
+We selected Linux 3.18 for our experiment.
 In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.
@@
 Some of the kernel conﬁguration options may have an impact on real-time latencies.
-These options include all options under CPU Power Management, APM support, and Opportunistic sleep.
-Additionally, most debug options in Kernel hacking section lead to increased latencies.
-Those options are disabled before compilation.
+These options include Power Management, especially CPU frequency scaling, value of HZ, NUMA conﬁguration and so on.
+Additionally, most debug options (Kernel hacking section) lead to increased latencies.
+We disabled these config options before compilation.
 
@@
 It is used to differentiate timers on the target context they activate, among IRQ(handler), kernel and user threads, anticipating the next timer shot accordingly, so that such context is activated as close as possible to the ideal time.
-The gravity values can be set in the file `/proc/xenomai/latency` on Xenomai-2, `/proc/xenomai/clock/coreclk` on Xenomai-3 with root privilege.
+The gravity values can be set in the file \begin{verbatim}/proc/xenomai/latency on Xenomai-2, /proc/xenomai/clock/coreclk
+\end{verbatim} on Xenomai-3 with root privilege.
 Furthermore, Xenomai-3 has an autotune function that runs a series of internal calibration tests for estimating the most appropriate gravity values for its real-time clock timer, retaining the final values.

### 2015-10-20 paper.tex
Combine 2 kernel config section into one
config/patch table not yet added

--- 2015-10-20 paper.tex
@@
 Xenomai 3 is the new architecture of the real-time framework running seamlessly side-by-side Linux as a dual-kernel system like Xenomai 2, or natively over mainline Linux kernels supplemented by the PREEMPT\_RT efforts to meet stricter response time requirements than standard kernel preemption would bring.
-In this presentation, we will evaluate the performances of Xenomai 3 running with both configurations and analyze the various benchmarks for ARM Cortex-A series.
+In this presentation, we will evaluate the performances of Xenomai 3 running with dual-kernel configuration and analyze the various benchmarks for ARM Cortex-A series.
 Xenomai 3 introduces some optimizations over RTOS API emulation, thread-to-thread communications, and significantly lower overhead with dual-kernel configurations.
@@
 \subsubsection{Hardware}
-BeagleBone Black, an effective embedded platform with ARM Cortex-A8 processor, capable of running Linux and Xenomai (both 2 and 3), consisting of a single processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
+For the testing platform, we used the BeagleBone Black.
+BeagleBone Black is an effective embedded platform with ARM Cortex-A8 processor, capable of running Linux and Xenomai (both 2 and 3), consisting of a single processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
 
-\subsubsection{Kernel}
-A Linux kernel that can be patched with PREEMPT\_RT, Xenomai 2 and Xenomai 3 is needed for the experiment (Xenomai 3 has to run on Linux kernel 3.10 or later versions).
-Linux 3.14 is selected for our experiment.
-In some cases when the patches couldn't be successfully applied on the kernel, we tried to resolve the conflicts manually.
+\subsubsection{Linux Kernel}
+We installed a Debian Linux image\cite{debian} on the beaglebone, with hardware-specific linux kernel from\cite{kernel}.
+Kernel version 3.14.39 were chosen due to it's compatibility with all kernel configurations.
+Four distinct kernel configurations are used for the experiment, as summarized in table\ref{table:config}. Kernel are patched using git merge first, and remaining conflicts are resolved manually.
 
-\subsubsection{Kernel configuration }
-Some of the kernel conﬁguration options may have an impact on real-time latencies.
+Kernel conﬁguration options are mostly left as default.
+However, some of the options may have an impact on real-time latencies.
 These options include all options under CPU Power Management, APM support, and Opportunistic sleep.
 Additionally, most debug options in Kernel hacking section lead to increased latencies.
-Those options are disabled before compilation.
+Those options are turned off before compilation.
+
+% TODO : add config table
 
@@
 	\bibitem {sel4}{\it http://ssrg.nicta.com.au/projects/seL4/}
+	\bibitem {debian}{\it http://debian.beagleboard.org/images/bone-debian-7.5-2014-05-14-2gb.img.xz}
+	\bibitem {kernel}{\it https://github.com/beagleboard/linux}
 \end{thebibliography}

### 2015-10-20 paper.tex
Add : config table
\table tag doesn't seems to work properly (not visible when added)
still can't reference table using \ref tag (line 153)

@@
 
-% TODO : add config table
+\begin{tabular}{|l| p{3cm} |l|}
+\hline
+Kernel & Patches & source\\ \hline
+mainline   & none & n/a \\ \hline
+PREEMPT\_RT & patch-3.14.39-rt37 & \cite{p-rt} \\ \hline
+Xenomai 2  & ipipe-core-3.14.39-arm-9 + xenomai v2.6.4 (2015-07-13 HEAD) & \cite{p-ipipe} \cite{git-x2.6} \\ \hline
+Xenomai 3  & ipipe-core-3.14.39-arm-9 + xenomai v3.0  & \cite{p-ipipe} \cite{git-x3} \\ \hline
+\end{tabular}
 
@@
 	\bibitem {kernel}{\it https://github.com/beagleboard/linux}
+	\bibitem {p-rt}{\it https://www.kernel.org/pub/linux/kernel/projects/rt/3.14/}
+	\bibitem {p-ipipe}{\it http://download.gna.org/adeos/patches/v3.x/arm/ipipe-core-3.14.39-arm-9.patch}
+	\bibitem {git-x2.6}{\it http://git.xenomai.org/xenomai-2.6.git/}
+	\bibitem {git-x3}{\it http://git.xenomai.org/xenomai-3.git/}
 \end{thebibliography}

### 2015-10-20 paper.tex
improve multiple author list

@@
 \usepackage{sectsty}
+\usepackage{authblk}
 
@@
 
-\author{\large
-{\bf Ching-Chun (Jim) Huang, Che-Kang Wu }\\
-Department of Computer Science and Information Engineering, \\
+\author[*]{\large
+{\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
+\author[*]{\large
+{\bf Che-Kang Wu}\thanks{an4006048$@$mail.ncku.edu.tw}}
+\author[**]{\large
+{\bf Chan-Hsiang Lin}\thanks{r04943031$@$ntu.edu.tw}}
+\affil[*]{Department of Computer Science and Information Engineering, \\
 National Cheng Kung University, Taiwan\\
-No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\
-\vspace{8mm}
-jserv$@$ccns.ncku.edu.tw, an4006048$@$mail.ncku.edu.tw\\
-{\bf Chan-Hsiang Lin}\\
-Department of Electrical and Electronic Engineering, National Taiwan University\\
-No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)\\
-\vspace{8mm}
-r04943031$@$ntu.edu.tw\\
-}
+No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
+\affil[**]{Department of Electrical and Electronic Engineering, \\
+National Taiwan University\\
+No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)}
 \date{}

### 2015-10-20 paper.tex
author: properly add new line

@@
 {\bf Chan-Hsiang Lin}\thanks{r04943031$@$ntu.edu.tw}}
-\affil[*]{Department of Computer Science and Information Engineering, \\
-National Cheng Kung University, Taiwan\\
+\affil[*]{Department of Computer Science and Information Engineering,
+\newline
+National Cheng Kung University, Taiwan
+\newline
 No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
-\affil[**]{Department of Electrical and Electronic Engineering, \\
-National Taiwan University\\
+\affil[**]{Department of Electrical and Electronic Engineering,
+\newline
+National Taiwan University
+\newline
 No.1, Sec. 4, Roosevelt Road, Taipei, Taiwan (R.O.C.)}

### 2015-10-20 paper.tex
Not include eps files anymore. Increase latency graph legends spacing and fonts.
author: adjust the order to be consistent
make \cite work again
Modify experiment paragraphs

@@
 {\bf Ching-Chun (Jim) Huang}\thanks{jserv@ccns.ncku.edu.tw}}
+\author[**]{\large
+{\bf Chan-Hsiang Lin}\thanks{r04943031$@$ntu.edu.tw}}
 \author[*]{\large
 {\bf Che-Kang Wu}\thanks{an4006048$@$mail.ncku.edu.tw}}
-\author[**]{\large
-{\bf Chan-Hsiang Lin}\thanks{r04943031$@$ntu.edu.tw}}
 \affil[*]{Department of Computer Science and Information Engineering,
@@
 \section{Experiment}
-
-\subsection{Purpose}
-1. Compare the performance of Xenomai with baseline Linux kernel and PREEMPT\_RT patched kernel
-2. Compare the performance of Xenomai-2 and Xenomai-3
+There are two objectives we wish to complete in our experiment.
+First, compare the performance of Xenomai with baseline Linux kernel and PREEMPT\_RT patched kernel to decide which configuration has better realtime capability.
+Second, try to validate whether Xenomai-3 has improved its realtime performance.
+The details are described in following sub-chapters.
 \subsection{Environment Setup}
-
+Because building and transporting operating systems on embedded devices is complicated.
+In order for other people to re-do the experiment, it needs proper setup and documentation.
+We will elaborate on different parts of the experiment setup.
 \subsubsection{Hardware}
@@
 BeagleBone Black is an effective embedded platform with ARM Cortex-A8 processor, capable of running Linux and Xenomai (both 2 and 3), consisting of a single processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
-
 \subsubsection{Linux Kernel}
@@
 Xenomai 3  & ipipe-core-3.14.39-arm-9 + xenomai v3.0  & \cite{p-ipipe} \cite{git-x3} \\ \hline
+\label{table:config}
 \end{tabular}
@@
 It is used to differentiate timers on the target context they activate, among IRQ(handler), kernel and user threads, anticipating the next timer shot accordingly, so that such context is activated as close as possible to the ideal time.
-The gravity values can be set in the file \begin{verbatim}/proc/xenomai/latency on Xenomai-2, /proc/xenomai/clock/coreclk
+The gravity values can be set in the file \begin{verbatim}/proc/xenomai/latency\end{verbatim} on Xenomai-2, and in the file \begin{verbatim}/proc/xenomai/clock/coreclk
 \end{verbatim} on Xenomai-3 with root privilege.
@@
 \begin{center}
-\includegraphics[width=8cm]{img/cyclictest_idle.jpg}
+\includegraphics[width=6cm]{img/cyclictest_idle.jpg}
 \caption{Cyclictest with no stress.}
@@
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[H]
 \begin{center}
-\includegraphics[width=8cm]{img/cyclictest_stress.jpg}
+\includegraphics[width=6cm]{img/cyclictest_stress.jpg}
 \caption{Cyclictest with stress.}
-\label{cyclictest-tress}
+\label{cyclictest-stress}
 \end{center}
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[H]
 \begin{center}
-\includegraphics[width=8cm]{img/latency_idle.jpg}
-\caption{Latency with no stress.}
-\label{latency-idle}
+\includegraphics[width=6cm]{img/x2-idle.png}
+\caption{Latency with no stress on Xenomai-2.}
+\label{x2-latency-idle}
 \end{center}
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[H]
 \begin{center}
-\includegraphics[width=8cm]{img/latency_stress.jpg}
-\caption{Latency with no stress.}
-\label{latency-stress}
+\includegraphics[width=6cm]{img/x2-cpu.png}
+\caption{Latency with stress on Xenomai-2.}
+\label{x2-latency-stress}
 \end{center}
 \end{figure}
-
-\epsin{cyclic-idle}{80}{fig2:f2}{Cyclictest Idle}
-\epsin{cyclic-cpu}{80}{fig3:f3}{Cyclictest stressed}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=6cm]{img/x3-idle.png}
+\caption{Latency with no stress on Xenomai-3.}
+\label{x3-latency-idle}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=6cm]{img/x3-cpu.png}
+\caption{Latency with stress on Xenomai-3.}
+\label{x3-latency-stress}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{tabular}{|l|c|r|r|}
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \begin{thebibliography}{9}%use this if you have <=9 bib refs

### 2015-10-20 paper.tex
Change tables - caption bug not fixed

@@
 Kernel version 3.14.39 were chosen due to it's compatibility with all kernel configurations.
-Four distinct kernel configurations are used for the experiment, as summarized in table\ref{table:config}. Kernel are patched using git merge first, and remaining conflicts are resolved manually.
+Four distinct kernel configurations are used for the experiment, as summarized in table below. Kernel are patched using git merge first, and remaining conflicts are resolved manually.
 
@@
 \hline
-Kernel & Patches & source\\ \hline
+Kernel & Patches & Source\\ \hline
 mainline   & none & n/a \\ \hline
@@
 Xenomai 3  & ipipe-core-3.14.39-arm-9 + xenomai v3.0  & \cite{p-ipipe} \cite{git-x3} \\ \hline
-\label{table:config}
-\end{tabular}
+\end{tabular}\\
 
@@
 Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
-\end{tabular}
-
+\end{tabular} \\
+Table 1: cyclictest result on different kernel setups, in microseconds\\
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{tabular}{|l|r|r|r|}
@@
 Xenomai 3 & 6 & 16 & 37 \\ \hline
-\end{tabular}
+\end{tabular}\\
+Table 2: latency result on different kernel setups, in microseconds\\
 

### 2015-10-20 paper.tex
delete uunnecessary files

@@
 \end{tabular}\\
-
+Table 1: Different kernel configurations for the experiment\\
 \subsubsection{Pre-experiment Settings}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{tabular}{|l|c|r|r|}
-\hline
-\multirow{2}{*}{} & \multicolumn{3}{c|}{user} \\ \cline{2-4} 
- & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
-Xenomai 2 & 8.541 & 9.458 & 34.583 \\ \hline
-Xenomai 3 & 8.043 & 8.853 & 33.023 \\ \hline
-& \multicolumn{3}{c|}{kernel}      \\ \hline
-Xenomai 2 & 6.965 & 7.708 & 27.821 \\ \hline
-Xenomai 3 & 5.567 & 6.479 & 25.577 \\ \hline
-& \multicolumn{3}{c|}{timer-irq}   \\ \hline
-Xenomai 2 & 2.129 & 2.654 & 11.343 \\ \hline
-Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
-\end{tabular} \\
-Table 1: cyclictest result on different kernel setups, in microseconds\\
-%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{tabular}{|l|r|r|r|}
@@
 \end{tabular}\\
-Table 2: latency result on different kernel setups, in microseconds\\
+Table 2: cyclictest result on different kernel setups, in microseconds\\
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{tabular}{|l|c|r|r|}
+\hline
+\multirow{2}{*}{} & \multicolumn{3}{c|}{user} \\ \cline{2-4} 
+ & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
+Xenomai 2 & 8.541 & 9.458 & 34.583 \\ \hline
+Xenomai 3 & 8.043 & 8.853 & 33.023 \\ \hline
+& \multicolumn{3}{c|}{kernel}      \\ \hline
+Xenomai 2 & 6.965 & 7.708 & 27.821 \\ \hline
+Xenomai 3 & 5.567 & 6.479 & 25.577 \\ \hline
+& \multicolumn{3}{c|}{timer-irq}   \\ \hline
+Xenomai 2 & 2.129 & 2.654 & 11.343 \\ \hline
+Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
+\end{tabular} \\
+Table 3: latency result on different kernel setups, in microseconds\\
 

### 2015-10-20 paper.tex
mention Xenomai 3

@@
 
-This paper would be a report on performance measurements among upstream Linux real-time enhancements and Xenomai official stable release (both version 2 and 3 series), and and the benchmarks show that the maximum response time to external interrupts of the dual kernel configurations for Xenomai 3 is almost twice as PPREEMPT\_RT, that more predictable handling on multiple incoming interrupts where Xenomai 3 supports both configurations interchangeably.
+This paper would be a report on performance measurements between upstream Linux real-time enhancements and Xenomai official stable release (both version 2 and 3 series), and the benchmarks show that the maximum response time to external interrupts of the dual kernel configurations for Xenomai 3 is almost twice as PPREEMPT\_RT, that implies more predictable handling on multiple incoming interrupts where Xenomai 3 supports both configurations interchangeably.
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% SECTION (REQUIRED)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+The default Linux is designed to optimize for total system throughput, rather than for interactivity or the ability to perform real-time work.
 Historically speaking, there are two typical approaches to modifying the standard Linux kernel into a real-time kernel.
-The first uses an extra small real-time executive \cite{rtai} or microkernel \cite{sel4} which runs the para-virtualized Linux kernel as a task.
-The small real-time executive takes control over the system for real-time processes and is responsible for scheduling real-time tasks, interrupt handling and scheduling Linux.
+The first introduces an extra small real-time executive \cite{rtai} or microkernel \cite{sel4} which runs the modified Linux kernel as a task.
+The small real-time executive, sometimes referred to \textit{co-kernel}, takes control over the system for real-time processes and is responsible for scheduling real-time tasks, interrupt handling and scheduling Linux.
 With these changes it is possible to let a real-time task run on the CPU without the Linux kernel being able to interrupt the task.
@@
 
-With the second approach, changes are made the Linux kernel in order to be real-time. This include changes as real-time
-scheduling and adding preemption to the kernel.
+Another approach is to make the Linux kernel itself more real-time by reducing the durations for which high-priority operations can be blocked, at the cost of reducing overall throughput.
+\textit{PREEMPT\_RT} \cite{linux-rt}, maintained separately from the Linux upstream, results in pure kernel implementation, and neither application programming interface (API) nor application binary interface (ABI) change is required.
+PREEMPT\_RT allows the use of existing Linux device drivers from real-time applications by making many spinlock-guarded regions preemptible, moving IRQ handlers into threads, and adding various other real-time features.
 
-In this section we briefly present the Xenomai real-time framework for Linux, and the Adaptive Domain Environment for Operating System (Adeos) layer, which allows Xenomai and Linux to run on the same hardware platform.
+In this section we briefly present the Xenomai \cite{xenomai} real-time framework for Linux, and its base real-time executive, Adaptive Domain Environment for Operating System (Adeos) nanokernel \cite{adeos}, which allows Xenomai and Linux to run on the same hardware.
 
-To provide an objective metric, we run processes on the test system, but measure their performance using an external measurement system which runs a C program on bare metal.
+\subsection{Adeos nanokernel}
 
-\subsection{Adeos layer}
-
-\textit{Adeos} is a resource virtualization layer, allowing multiple entities called \textit{domains}, that can be seen as complete operating systems, to run  simultaneously on the same hardware platform.
-
-Adeos domains can compete with each other for receiving system generated \textit{events}.
+\textit{Adeos} is a resource virtualization layer, allowing multiple entities called \textit{domains}, which can compete with each other for receiving system generated \textit{events}.
 Those events can be incoming external (or virtually generated) interruptions, Linux system calls invocations, or various kernel-code-related events like context switches.
@@
 
-In the case of a Xenomai RTOS running with a Linux kernel, the Adeos pipeline and the organization of the domains is depicted in Figure "EventPipeline".
-In the pipeline,  we can see that Xenomai has the highest priority, so it can handle and manage first the events before passing them to the Linux kernel.
-The events can also be blocked by the interrupt shield, preserving the real-time framework from latencies due to event management by the Linux kernel.
-Throughout this mechanism, Xenomai framework can provide real-time guarantees.
+Adeos is maintained by its I-pipe software.
+In Xenomai parlance, the I-pipe and Adeos both refer to the almost same code, that makes a Linux kernel able to host a secondary kernel exhibiting real-time properties (e.g.
+Xenomai), on the same hardware.
+I-pipe is a kernel patch applied to a regular Linux kernel, which among other services, guarantees delivery of external interrupts to Xenomai with very low latency.
+However, since Xenomai 3 supports PREEMPT\_RT, I-pipe is dependant only for running Xenomai in a dual kernel configuration.
 
@@
 
-Xenomai provides a kernel-based Application Programming Interface (API) for real-time applications.
-A user-land API is also available, at the cost of longer latencies.
-Xenomai introduces the concept of \textit{skins}.
-Skins are source codes emulating proprietary APIs used for porting real-time applications from various RTOSs such as \textit{VxWorks}, \textit{pSOS}, etc.
+Xenomai provides a kernel-based API for real-time applications.
+A user-space API is also available, at the cost of longer latencies.
+Xenomai introduces the concept of \textit{skins} \cite{ChameleonRTOS}, emulating proprietary APIs used for migrating real-time applications from various RTOSs like \textit{VxWorks}, \textit{pSOS}, \textit{VRTX}, etc.
 to Xenomai.
-When designing a Xenomai application from scratch, the \textit{native} Xenomai skin can be used.
 
-All Xenomai skins rely on the \textit{nucleus}, the core of the RTOS, implementing all algorithms for real-time functionalities.
-Xenomai provides all standard services one can expect to find in a RTOS: task management, multiple scheduling algorithms, IPCs, etc.
+All Xenomai skins rely on the common the core of the RTOS, implementing all algorithms for real-time functionalities.
+Xenomai 3 provides all standard services one can expect to find in a classical RTOS such as handling interrupts and scheduling real-time threads, by means of two options: Cobalt and Mercury.
 
-\subsection{Time management in Xenomai}
-We focused in this project on periodic real-time tasks that make extensive use of timers. A commonly used skeleton for those tasks in Xenomai as follows :
+\subsection{Cobalt}
 
-%\vspace{-0.5cm}
-\begin{verbatim}
-void myRealTimeTask(void *arg) {
-  SetPeriodic(myself, period);
-  while(1) {
-    /* Do something */
-    wait_period();
-  }
-}
-\end{verbatim}
-%\vspace{-0.5cm}
+\textit{Cobalt}, distinguished in Xenomai 3, is the real-time extension, built into the Linux kernel, dealing with all time-critical activities on top of Adeos I-pipe.
+The Cobalt core has higher priority over the native kernel activities and has the same behaviour as what Xenomai 2 delivers real-time.
+For both Cobalt (as known as \textit{dual kernel} configurationin Xenomai 3) and Xenomai 2, the Linux kernel receives only virtual interrupt events, and those only after higher-priority software (e.g.
+the Xenomai layer) has had an opportunity to respond first.
+Similarly, when the Linux kernel blocks interrupt handlers, it does so only for itself; high-priority Xenomai threads will receive their events from the I-pipe on schedule.
 
-The \verb+SetPeriodic()+ function creates and starts a timer related to the calling task, with a period (in clock ticks) equals to the specified parameter.
-The global tick management function notifies the timer each time a clock tick occurs.
-When reaching wake up time, the timer executes a handler placing the task in the ready state.
+In the dual kernel configuration of Xenomai 3, all the RTOS APIs Xenomai provides interface with the Cobalt core, and only those APIs are deemed real-time capable, including the subset of POSIX 1003.1c \cite{posix-1003-1c} services implemented by \textit{libcobalt}, which was named after \textit{nucleus} in Xenomai 2.
 
-\section{Experiment}
-There are two objectives we wish to complete in our experiment.
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=8cm]{img/x3-cobalt.png}
+\caption{Xenomai 3 dual kernel configuration}
+\label{xenomai3-coblat}
+\end{center}
+\end{figure}
+
+\subsection{Mercury}
+
+\textit{Mercury} was derived on the past experiment, \textit{Xenomai/SOLO} project \cite{xenomai-solo}, as an intermediate step towards Xenomai 3.
+Xenomai/SOLO project was the clean-room re-implementation of the building blocks that connect an emulator with the underlaying RTOS with special respect to the requirements and semantics of the native Linux kernel.
+The VxWorks emulator was the first one built over the Xenomai/SOLO project, as proof of concept (PoC), providing the VxWorks core API that can be used to port existing VxWorks applications to native Linux.
+
+Xenomai 2 provides skins to emulate traditional RTOS, such as VxWorks and pSOS, and a number of projects have been migrated smoothly from one of the supported traditional RTOS to Xenomai.
+In order to use a similar approach to migrate traditional RTOS projects to native Linux as well, Xenomai 3.x was launched.
+Thus, the single kernel configuration, Mercury, in Xenomai 3 does rely on the real-time capabilities of the native Linux kernel.
+Often, applications will require the PREEMPT\_RT extension to be enabled in the target kernel, for delivering real-time services.
+
+PREEMPT\_RT is not mandatory, however, and Mercury depends on the application requirements with respect to responsiveness and maximum jitter; some may even tolerate a certain percentage of deadline misses.
+
+In this single kernel configuration, all the non-POSIX RTOS APIs Xenomai provides are accurately emulated over the native threading library (preferably NPTL).
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=8cm]{img/x3-mercury.png}
+\caption{Xenomai 3 single kernel configuration}
+\label{xenomai3-coblat}
+\end{center}
+\end{figure}
+
+Xenomai 3 offers both dual-kernel and native option, and it deploys same Alchemy \cite{x3-applications} API on Cobalt/I-pipe and PREEMPT\_RT.
+Xenomai 3 was designed for tight latency requirement, configuration flexibility, and system compatibility.
+
+\section{Performance Evaluation}
+There are two objectives for performance evaluations.
 First, compare the performance of Xenomai with baseline Linux kernel and PREEMPT\_RT patched kernel to decide which configuration has better realtime capability.
@@
 	\bibitem {sel4}{\it http://ssrg.nicta.com.au/projects/seL4/}
+	\bibitem {linux-rt}{\it http://git.kernel.org/cgit/linux/kernel/git/rt/}
+	\bibitem {xenomai}{\it http://xenomai.org/}
+	\bibitem {adeos} Karim Yaghmour. Adaptive Domain Environment for Operating Systems.\\
+	    \url{http://www.opersys.com/ftp/pub/Adeos/adeos.pdf}
+	\bibitem {ChameleonRTOS}{\it http://www.xenomai.org/documentation/slides/Xenomai-OSMB-2007-01.pdf}
+	\bibitem {posix-1003-1c}{\it http://standards.ieee.org/findstds/interps/1003-1c-95\_int/}
+	\bibitem {xenomai-solo}{\it https://www.osadl.org/Xenomai-SOLO.xenomai-solo.0.html}
+	\bibitem {x3-applications}{\it http://xenomai.org/running-applications-with-xenomai-3-x/}
 	\bibitem {debian}{\it http://debian.beagleboard.org/images/bone-debian-7.5-2014-05-14-2gb.img.xz}

### 2015-10-21 paper.tex
improve test descriptions

@@
 There are two objectives for performance evaluations.
-First, compare the performance of Xenomai with baseline Linux kernel and PREEMPT\_RT patched kernel to decide which configuration has better realtime capability.
-Second, try to validate whether Xenomai-3 has improved its realtime performance.
-The details are described in following sub-chapters.
-\subsection{Environment Setup}
-Because building and transporting operating systems on embedded devices is complicated.
-In order for other people to re-do the experiment, it needs proper setup and documentation.
-We will elaborate on different parts of the experiment setup.
+First, comparing the performance of Xenomai with mainline Linux kernel and PREEMPT\_RT to exploit the real-time capability from system view.
+Second, trying to quantize the performance improvements and potential degradation of Xenomai 3.
+
 \subsubsection{Hardware}
-For the testing platform, we used the BeagleBone Black.
-BeagleBone Black is an effective embedded platform with ARM Cortex-A8 processor, capable of running Linux and Xenomai (both 2 and 3), consisting of a single processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
-\subsubsection{Linux Kernel}
-We installed a Debian Linux image\cite{debian} on the beaglebone, with hardware-specific linux kernel from\cite{kernel}.
-Kernel version 3.14.39 were chosen due to it's compatibility with all kernel configurations.
-Four distinct kernel configurations are used for the experiment, as summarized in table below. Kernel are patched using git merge first, and remaining conflicts are resolved manually.
+\textit{BeagleBone Black}\cite{bbb} is selected as our major testing hardware platform powered by \textit{TI AM335x} \cite{am335x}, and it is an effective embedded platform, capable of running Linux and Xenomai (both 2 and 3), consisting of a single 1GHz ARM Cortex-A8 processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
 
-Kernel conﬁguration options are mostly left as default.
-However, some of the options may have an impact on real-time latencies.
-These options include all options under CPU Power Management, APM support, and Opportunistic sleep.
-Additionally, most debug options in Kernel hacking section lead to increased latencies.
-Those options are turned off before compilation.
+Beaglebone Black is community-supported development platform, and active Linux kernel maintenance enables us to perform further experiments and participate in technical discussions.
+TI AM335x is used widely in industrial automation, providing an extensive, reliable solution portfolio ranging from robust microcontrollers to ARM based microprocessors.
+
+\subsubsection{Software Installation}
+Debian GNU/Linux image 2014-05-14 \cite{debian} was installed on the BeagleBone Black, with hardware-specific Linux kernel tree from official BeagleBone kernel repository \cite{kernel}.
+We selected kernel version 3.14.39 due to its compatibility with all kernel configurations after our early evaluations.
+
+Four distinct Linux kernel configurations are used for the experiments, as summarized in table below. Kernel are patched using git merge first, and remaining conflicts are resolved manually.
+
+The kernel conﬁguration options are mostly following the default.
+However, some of the default configuration may have an impact on real-time latencies, such as the ones about CPU Power Management, APM support, and opportunistic sleep.
+Additionally, most debugging facilities in Kernel hacking section lead to increased latencies.
+Those problematic options are turned off manually in advance.
 
@@
 Kernel & Patches & Source\\ \hline
-mainline   & none & n/a \\ \hline
+mainline   & N/A & N/A \\ \hline
 PREEMPT\_RT & patch-3.14.39-rt37 & \cite{p-rt} \\ \hline
-Xenomai 2  & ipipe-core-3.14.39-arm-9 + xenomai v2.6.4 (2015-07-13 HEAD) & \cite{p-ipipe} \cite{git-x2.6} \\ \hline
-Xenomai 3  & ipipe-core-3.14.39-arm-9 + xenomai v3.0  & \cite{p-ipipe} \cite{git-x3} \\ \hline
+Xenomai 2  & ipipe-core-3.14.39-arm-9 + xenomai v2.6.4 (Jul 13, 2015; HEAD) & \cite{p-ipipe} \cite{git-x2.6} \\ \hline
+Xenomai 3  & ipipe-core-3.14.39-arm-9 + xenomai v3.0 (Oct 8, 2015) & \cite{p-ipipe} \cite{git-x3} \\ \hline
 \end{tabular}\\
 Table 1: Different kernel configurations for the experiment\\
-\subsubsection{Pre-experiment Settings}
-We tried to measure the latencies under 2 conditions - IDLE and CPU-STRESSED.
-In the IDLE experiment, in order to create such test environment, some redundant user processes were eliminated.
-While in the CPU-STRESSED condition, these process are also killed, and we used the 'stress' command to keep the CPU busy.
+
+\subsubsection{Prerequisites for Experiments}
+We tried to measure the latencies under 2 conditions: IDLE and CPU-STRESSED.
+In the IDLE condition, in order to create such test environment, some redundant user processes were eliminated.
+While in the CPU-STRESSED condition, these process are also forcely killed, and we used the \textit{stress}\cite{stress} utility to keep the CPU busy.
 The command to kill these processes are written in the test script.
@@
 	\bibitem {x3-applications}{\it http://xenomai.org/running-applications-with-xenomai-3-x/}
+	\bibitem {bbb}{\it http://beagleboard.org/BLACK}
+	\bibitem {am335x}{\it http://www.ti.com/lsds/ti/processors/sitara/arm\_cortex-a8/am335x/overview.page}
 	\bibitem {debian}{\it http://debian.beagleboard.org/images/bone-debian-7.5-2014-05-14-2gb.img.xz}
@@
 	\bibitem {git-x3}{\it http://git.xenomai.org/xenomai-3.git/}
+	\bibitem {stree}{\it http://people.seas.harvard.edu/~apw/stress/}
 \end{thebibliography}

### 2015-10-21 paper.tex
improve description and fix links

@@
 
-\section{Performance Evaluation}
+\section{Measurement system design}
 There are two objectives for performance evaluations.
@@
 Additionally, most debugging facilities in Kernel hacking section lead to increased latencies.
-Those problematic options are turned off manually in advance.
+Those problematic options are disabled manually during the whole experiments.
 
@@
 We tried to measure the latencies under 2 conditions: IDLE and CPU-STRESSED.
-In the IDLE condition, in order to create such test environment, some redundant user processes were eliminated.
-While in the CPU-STRESSED condition, these process are also forcely killed, and we used the \textit{stress}\cite{stress} utility to keep the CPU busy.
-The command to kill these processes are written in the test script.
+In the IDLE condition, in order to create such test environment, some non-essential user processes were eliminated.
+While in the CPU-STRESSED condition, these process are also forcely killed, and we used the \textit{stress} \cite{stress} utility to keep the CPU busy.
+The commands to kill these processes are written in the test script.
 
   The gravity values is the shortest time the platform needs to deliver an IRQ to a Xenomai interrupt handler, a RTDM task running in kernel space, or a user-space task.
-It is used to differentiate timers on the target context they activate, among IRQ(handler), kernel and user threads, anticipating the next timer shot accordingly, so that such context is activated as close as possible to the ideal time.
-The gravity values can be set in the file \begin{verbatim}/proc/xenomai/latency\end{verbatim} on Xenomai-2, and in the file \begin{verbatim}/proc/xenomai/clock/coreclk
-\end{verbatim} on Xenomai-3 with root privilege.
-Furthermore, Xenomai-3 has an autotune function that runs a series of internal calibration tests for estimating the most appropriate gravity values for its real-time clock timer, retaining the final values.
-Because Xenomai-2 doesn't have an autotune function and it has only one gravity value for all the 
-coreclocks, we decided to manually tune all the coreclock values in both Xenomai-2 and Xenomai-3 to zero, so that we can later compare the results on the same basis.
+It is used to differentiate timers on the target context they activate, among IRQ (handlers), kernel and user threads, anticipating the next timer shot accordingly, so that such context is activated as close as possible to the ideal time.
+The gravity values can be set in the file \begin{verbatim}/proc/xenomai/latency
+\end{verbatim} on Xenomai 2, and in the file
+\begin{verbatim}/proc/xenomai/clock/coreclk
+\end{verbatim} on Xenomai 3 with root privilege.
+Furthermore, Xenomai 3 provides an \textit{autotune} tool running a series of internal calibration tests for estimating the most appropriate gravity values for its real-time clock timer, retaining the final values.
 
-In our experiments, the kernel build were stored in different SD cards.
-The fact that different external storage devices have different access specs could affect the result.
-In order to eliminate the uncertainties, and for the sake of preventing the test process's pages being swapped into disk, we locked all the test process's pages inside memory.
-In cyclictest, this achieved by specifying the '-m' option in the command.
-On the other hand, latency is already executed in a memory locked condition.
+Because Xenomai 2 does not provide the corresponding autotune tool, and it has only one gravity value for all the coreclocks, we decided to manually tune all the coreclock values in both Xenomai 2 and Xenomai 3 to zero, so that we can compare the results on the same basis later
 
-\subsection{Testing Process}
+In our experiments, the kernel build were persistent in different SD/MMC media.
+The fact that different external storage devices have different access speeds could affect the final results.
+In order to eliminate the uncertainties and prevent the test process' pages from being swapped into disk, we locked all the test processes' pages inside memory.
+While using \textit{cyclictest} tool, we can achieve by specifying the '-m' option along with the command.
+On the other hand, we exclude the known latency factors and execute programs within one memory locking condition.
 
-\subsubsection{Scenario}
+\subsection{Performance Evaluation}
+
+\subsubsection{Test scenario}
 The goal of the experiment is to evaluate the realtime performances of Mainline Linux, PREEMPT\_RT, 
@@
 	\bibitem {git-x3}{\it http://git.xenomai.org/xenomai-3.git/}
-	\bibitem {stree}{\it http://people.seas.harvard.edu/~apw/stress/}
+	\bibitem {stress}{\it http://people.seas.harvard.edu/~apw/stress/}
 \end{thebibliography}

### 2015-10-21 paper.tex
lock memory
print microsecond correctly

@@
 \usepackage{authblk}
-
+\usepackage{textcomp}
 \renewcommand{\refname}{}
@@
 While using \textit{cyclictest} tool, we can achieve by specifying the '-m' option along with the command.
-On the other hand, we exclude the known latency factors and execute programs within one memory locking condition.
+On the other hand, we exclude the known latency factors and execute programs within the memory-locked environment.
 
@@
 
-From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 us) than on Xenomai-2(below 3 us).
+From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 \textmu s) than on Xenomai-2(below 3 \textmu s).
 While this is not an occasional case(the same experiment was ran a couple times), we tried to look into the test code of latency to figure out the cause of this phenomenon.
@@
 \subsection{Experiment Result Analysis}
-Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 us in idle situation, 18 us in stressed situation.
-And in the worse case, the latency is below 50 us.
-Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 us and can't guarantee a 50 us max latency (Actually in some cases the latency will exceed 100 us in stressed condition).
+Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 \textmu s in idle situation, 18 \textmu s in stressed situation.
+And in the worse case, the latency is below 50 \textmu s.
+Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 \textmu s and can't guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 us in stressed condition).
 As for mainline Linux, the max latency easily exceeds 1 ms.

### 2015-10-21 paper.tex
fix microsecond

@@
 \subsubsection{Test scenario}
-The goal of the experiment is to evaluate the realtime performances of Mainline Linux, PREEMPT\_RT, 
-Xenomai-2 and Xenomai-3. Also, we want to find out whether the newly released Xenomai-3.0 has improved in realtime capability, compared to Xenomai-2.6.4, the latest stable version of Xenomai-2.
+The goal of the experiment is to evaluate the realtime performances of mainline Linux kernel, PREEMPT\_RT, 
+Xenomai 2 and Xenomai 3. Also, we want to find out whether the newly released Xenomai-3.0 has improved in realtime capability, compared to Xenomai-2.6.4, the latest stable version of Xenomai 2.
+
 \subsubsection{Tools}
@@
 Latency is then measured by calculating the difference of the actual time elapsed with the predefined period.
+
 \subsubsection{Test Procedure}
@@
 \end{tabular}\\
-Table 2: cyclictest result on different kernel setups, in microseconds\\
+Table 2: cyclictest result on different kernel setups, in \textmu s\\
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{tabular} \\
-Table 3: latency result on different kernel setups, in microseconds\\
+Table 3: latency result on different kernel setups, in \textmu s\\
 

### 2015-10-21 paper.tex
revised cyclictest

@@
 \subsubsection{Test scenario}
-The goal of the experiment is to evaluate the realtime performances of mainline Linux kernel, PREEMPT\_RT, 
-Xenomai 2 and Xenomai 3. Also, we want to find out whether the newly released Xenomai-3.0 has improved in realtime capability, compared to Xenomai-2.6.4, the latest stable version of Xenomai 2.
+We prepared comprehensive statistics collection for the real-time performance results of mainline Linux kernel, PREEMPT\_RT, Xenomai 2 and Xenomai 3.
+In addition, we expect to figure out the performance benefits from the newly released Xenomai version 3.0, the first official release of Xenomai 3, comparing to Xenomai-2.6.4, the latest stable release of Xenomai 2.
+This new architecture of Xenomai 3 exhibits two real-time options, selected at build time.
+The dual kernel configuration of Xenomai 3, Cobalt, is a significant rework of the Xenomai 2 system.
+And, the single kernel natively over mainline Linux kernels, which can be supplemented by the PREEMPT\_RT to meet stricter response time requirements.
 
-\subsubsection{Tools}
-Cyclictest is a commonly-used latency benchmark.
-It is compatible with all the kernel setups we use (the recently Xenomai-3.0 release add cyclictest to its testsuite), therefore it's suitable for the purpose of measuring latencies for all setups.
-Latency is a test program for the Xenomai test suite.
-It can measure latencies under 3 modes - user task, kernel task, or timer IRQ.
+Since the single kernel configuration is built upon mainline kernel or PREEMPT\_RT, we do not have to measure its configuration separately because of the availability of PREEMPT\_RT in our benchmark matrix.
+
+\subsubsection{Performance Tools}
+\textit{Cyclictest}, maintained in \textit{rt-tests} \cite{rt-tests} package, is a commonly-used latency benchmark.
+It is compatible with all of the kernel setups we use (the recently Xenomai 3.0 release shipped with cyclictest in its testsuite), therefore it is suitable for the purpose of measuring latencies for all setups.
+
+\textit{Latency} is a test program provided by the Xenomai test suite (available in both Xenomai 2 and 3).
+It can measure latencies under 3 modes: \textit{user task}, \textit{kernel task}, or \textit{timer IRQ}.
 It launches the test procedure in one of the user-specified contexts.
@@
 \subsubsection{Test Procedure}
-Each experiment was run on the same hardware. Each was run for 20 minutes to generate approximately 1,000,000 samples. Test scripts were written to facilitate the experiment process.
+Each experiment was run on the same Beaglebone Black hardware device.
+Each was run for 20 minutes to generate approximately 1,000,000 samples.
+Test scripts were written to facilitate the experiment process.
+
 \subsubsection{Test Load}
-As previously mentioned, we measure latencies under IDLE and CPU-STRESSED conditions. In the CPU-STRESSED condition, we called the "stress" process to exert pressure on the CPU.
+As previously mentioned, we measure latencies under IDLE and CPU-STRESSED conditions. In the CPU-STRESSED condition, we invoked the "stress" process to exert pressure on the CPU.
+
 \subsection{Experiment Result}
@@
 
-From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 \textmu s) than on Xenomai-2(below 3 \textmu s).
-While this is not an occasional case(the same experiment was ran a couple times), we tried to look into the test code of latency to figure out the cause of this phenomenon.
+From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai3 (over 3 \textmu s) than on Xenomai 2 (below 3 \textmu s).
+While this is not an occasional case (the same experiment was ran a couple times), we tried to look into the test code of latency to figure out the cause of this phenomenon.
 
@@
 	\bibitem {stress}{\it http://people.seas.harvard.edu/~apw/stress/}
+	\bibitem {rt-tests}{\it https://rt.wiki.kernel.org/index.php/Cyclictest}
 \end{thebibliography}

### 2015-10-21 paper.tex
show microsecond correctly

@@
 \subsection{Experiment Result Analysis}
-Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 \textmu s in idle situation, 18 \textmu s in stressed situation.
+Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 \textmu s in idle condition, 18 \textmu s in stressed condition.
 And in the worse case, the latency is below 50 \textmu s.
-Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 \textmu s and can't guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 us in stressed condition).
+Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 \textmu s, which means it can not guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 \textmu s in stressed condition).
 As for mainline Linux, the max latency easily exceeds 1 ms.
-When comparing the performance of Xenomai-3 to Xenomai-2, we can see that the stats in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.
+When comparing the performance of Xenomai 3 to Xenomai 2, we can see that the statistics in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.
 

### 2015-10-21 paper.tex
mention Copperplate and avoid API level benchmarking

@@
 
+In Xenomai 3, with the introduction of the \textit{Copperplate} interface, which mediates between the real-time API / emulator of given application uses, and the underlying real-time core.
+That is, applications are able to run in either environments without visible code change.
+We do not intend to measure the overhead of \textit{Copperplate} interface or its implementation for the sake of measuring the system-level performance rather than API-oriented emulation.
+
 \subsubsection{Performance Tools}
@@
 \section{Conclusions}
-The trait of real time in RTLinux is closely related to hardware, So we can take full advantage of PC.
-The testing on our recorder showed that the average of interrupt response time is 10us, and the max  is 15us.
-This performance can satisfy this real time requirement of recorder completely and guarantee data integrity.
-With the high-performance and  great capacity hard disk using, the capacity of the RAID would reach over 1000GB, moreover, collected data don't loss even if one hard disk is demaged.
-
-We had done the test that  under the same hard platform, the recording speed has significantly enhanced in RTLinux than in Windows NT.
-RTLinux is free, open source, retractile, and transferable, so many OS can not bear comparison with it.
-RTLinux has been applied successful in our pre-demodulation Digital Recorder; moreover, it will be more widely used in the field of real-time control.
 

### 2015-10-21 paper.tex
initial conclusion

@@
 
-This paper would be a report on performance measurements between upstream Linux real-time enhancements and Xenomai official stable release (both version 2 and 3 series), and the benchmarks show that the maximum response time to external interrupts of the dual kernel configurations for Xenomai 3 is almost twice as PPREEMPT\_RT, that implies more predictable handling on multiple incoming interrupts where Xenomai 3 supports both configurations interchangeably.
+This paper would be a report on performance measurements between upstream Linux real-time enhancements and Xenomai official stable release (both version 2 and 3 series), and the benchmarks show that the maximum response time to external interrupts of the dual kernel configurations for Xenomai 3 is still better than PPREEMPT\_RT, that implies more predictable handling on multiple incoming interrupts where Xenomai 3 supports both configurations interchangeably.
 \end{abstract}
@@
 That is, applications are able to run in either environments without visible code change.
+
+The default interfaces have switched to being POSIX-based (Copperplate library) in Xenomai 3, so all other real-time APIs (or skins) are implemented on top of this.
+In particular, the Xenomai 2 native API (now called Alchemy) is a skin, while the POSIX API has been promoted from a skin to the standard interface.
 We do not intend to measure the overhead of \textit{Copperplate} interface or its implementation for the sake of measuring the system-level performance rather than API-oriented emulation.
@@
 \section{Conclusions}
+We have evaluated the performance of two approaches to make Linux being real-time: PREEMPT\_RT and Xenomai, diversely presented in the view of single kernel and dual-kernel configurations on single-core ARM Cortex-A8, along with general conclusions about when each kernel configuration.
+As for the dual kernel configuration of Xenomai 3, latency is still significantly better, but PREEMPT\_RT shows closer performance at least for Linux kernel 3.14 stable release while it enables to run same application on different platforms and migrate existing POSIX application to Linux systems.
+
+The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
+For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance.
+However, our results show some of the unexpected slowdown of Xenomai 3 comparing to Xenomai 2.
 

### 2015-10-21 paper.tex
work on the conclusion

@@
 The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
-For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance.
-However, our results show some of the unexpected slowdown of Xenomai 3 comparing to Xenomai 2.
+For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2.
+However, comparing to Xenomai 2, our results show the unexpected slowdown of timer-irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
+From our performance evaluation, Xenomai 3 is known as the most flexible real-time option.
 

### 2015-10-21 paper.tex
Add latency remark and fix table captian spacing

@@
 \end{tabular}\\
+vspace{4mm} \\
 Table 1: Different kernel configurations for the experiment\\
@@
 \end{tabular}\\
+vspace{4mm} \\
 Table 2: cyclictest result on different kernel setups, in \textmu s\\
+vspace{4mm} \\
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
+vspace{4mm} \\
 \end{tabular} \\
@@
 
-From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai3 (over 3 \textmu s) than on Xenomai 2 (below 3 \textmu s).
-While this is not an occasional case (the same experiment was ran a couple times), we tried to look into the test code of latency to figure out the cause of this phenomenon.
-
+From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 us) than on Xenomai-2(below 3 us).
+While this is not an occasional case(the same experiment was ran a couple of times), we tried to look into the test code of latency to figure out the cause of this phenomenon.
+In user-level mode, the measurement task is carried out by the function 'latency' inside the program; whereas in kernel or irq mode, the task is executed by issuing a Xenomai RTDM command such as
+\begin{verbatim}
+rt_dev_ioctl(benchdev, \
+RTTST_RTIOC_INTERM_BENCH_RES,&result); 
+\end{verbatim} 
+in an infinite loop to periodically launch timer and capture latencies. Unfortunately, we were unable to discover the reason for the discrepancy on the observed data.
 \subsection{Experiment Result Analysis}

### 2015-10-21 paper.tex
shorten the text

@@
 \end{tabular}\\
-vspace{4mm} \\
+\vspace{4mm} \\
 Table 1: Different kernel configurations for the experiment\\
@@
 \end{tabular}\\
-vspace{4mm} \\
+\vspace{4mm} \\
 Table 2: cyclictest result on different kernel setups, in \textmu s\\
-vspace{4mm} \\
+\vspace{4mm} \\
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 And in the worse case, the latency is below 50 \textmu s.
-Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 \textmu s, which means it can not guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 \textmu s in stressed condition).
+Meanwhile, the latency of PREEMPT\_RT has an averaged user-level latency more than 20 \textmu s, which means it can not guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 \textmu s in stressed condition).
 As for mainline Linux, the max latency easily exceeds 1 ms.
@@
 
-The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
+The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
 For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2.
-However, comparing to Xenomai 2, our results show the unexpected slowdown of timer-irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
-From our performance evaluation, Xenomai 3 is known as the most flexible real-time option.
+However, comparing to Xenomai 2, our results show the unexpected slowdown of timer irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration.
 

### 2015-10-21 paper.tex
fix some typos

@@
 
-The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
+The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
 For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2.
-However, comparing to Xenomai 2, our results show the unexpected slowdown of timer irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration.
+However, comparing to Xenomai 2, our results show the unexpected slowdown of timer-irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
+From our performance evaluation, Xenomai 3 is known as the most flexible real-time option.
 

### 2015-10-21 paper.tex
fix a typo

@@
 Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
-vspace{4mm} \\
+\vspace{4mm} \\
 \end{tabular} \\

### 2015-10-21 paper.tex
improve the syntax

@@
 
-Adeos is maintained by its I-pipe software.
+Adeos is maintained by its \textit{I-pipe} software.
 In Xenomai parlance, the I-pipe and Adeos both refer to the almost same code, that makes a Linux kernel able to host a secondary kernel exhibiting real-time properties (e.g.
@@
 
-Xenomai 3 offers both dual-kernel and native option, and it deploys same Alchemy \cite{x3-applications} API on Cobalt/I-pipe and PREEMPT\_RT.
+Xenomai 3 offers both dual-kernel and native option, and it deploys same \textit{Alchemy} \cite{x3-applications} API on Cobalt/I-pipe and PREEMPT\_RT.
 Xenomai 3 was designed for tight latency requirement, configuration flexibility, and system compatibility.
@@
 Mainline Linux & 39 & 43 & 1046  \\ \hline
-Preempt-RT & 16 & 21 & 52 \\ \hline
+Preempt\_RT & 16 & 21 & 52 \\ \hline
 Xenomai 2 & 8 & 9 & 41 \\ \hline
@@
 Mainline Linux & 39 & 52 & 1097 \\ \hline
-Preempt-RT & 18 & 25 & 62 \\ \hline
+Preempt\_RT & 18 & 25 & 62 \\ \hline
 Xenomai 2 & 8 & 19 & 45 \\ \hline

### 2015-10-21 paper.tex
Fix : \vspace in table 3

--- 2015-10-21 paper.tex
@@
 Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
+\end{tabular} \\
 \vspace{4mm} \\
-\end{tabular} \\
 Table 3: latency result on different kernel setups, in \textmu s\\

### 2015-10-21 paper.tex
improve the text

--- 2015-10-21 paper.tex
@@
 
-From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 us) than on Xenomai-2(below 3 us).
-While this is not an occasional case(the same experiment was ran a couple of times), we tried to look into the test code of latency to figure out the cause of this phenomenon.
-In user-level mode, the measurement task is carried out by the function 'latency' inside the program; whereas in kernel or irq mode, the task is executed by issuing a Xenomai RTDM command such as
+From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai 3 (over 3 \textmu s) than on Xenomai 2 (below 3 \textmu s).
+While this is not an occasional case, we already ensured the same experiment method was ran a couple of times, we tried to look into the test code of latency to figure out the cause of this phenomenon.
+In user-level mode, the measurement task is carried out by the function 'latency' inside the program; whereas in kernel or irq mode, the task is executed by issuing a Xenomai RTDM command such as:
 \begin{verbatim}
@@
 \end{verbatim} 
-in an infinite loop to periodically launch timer and capture latencies. Unfortunately, we were unable to discover the reason for the discrepancy on the observed data.
+in an infinite loop to periodically launch timer and capture latencies. Unfortunately, we were unable to discover the reason for the discrepancy on the observed data at that time.
+
 \subsection{Experiment Result Analysis}
@@
 For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2.
-However, comparing to Xenomai 2, our results show the unexpected slowdown of timer-irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
+However, comparing to Xenomai 2, our results show the unexpected slowdown of timer interrupt hanlding latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
 From our performance evaluation, Xenomai 3 is known as the most flexible real-time option.

### 2015-10-21 paper.tex
fix format

@@
 We selected kernel version 3.14.39 due to its compatibility with all kernel configurations after our early evaluations.
-
-Four distinct Linux kernel configurations are used for the experiments, as summarized in table below. Kernel are patched using git merge first, and remaining conflicts are resolved manually.
+Both Xenomai 3 Coblat and Xenomai 2 are working on the same I-pipe software for consistency.
 
@@
 Those problematic options are disabled manually during the whole experiments.
+
+Four distinct Linux kernel configurations are used for the experiments, as summarized in table below. Kernel are patched using git merge first, and remaining conflicts are resolved manually.
 
@@
 Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
+\end{tabular}\\
 \vspace{4mm} \\
-\end{tabular} \\
 Table 3: latency result on different kernel setups, in \textmu s\\
+\vspace{4mm}
 
@@
 However, comparing to Xenomai 2, our results show the unexpected slowdown of timer interrupt hanlding latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
-From our performance evaluation, Xenomai 3 is known as the most flexible real-time option.
+It is not clear why Cobalt in Xenomai 3 contributes to larger interrupt jitter measurement when the CPU is heavily loaded.
+This needs further investigation.
 

### 2015-10-21 paper.tex
Add : table of latency cpu-stressed data (table 4)
Caption of table might need to change

--- 2015-10-21 paper.tex
@@
 \vspace{4mm} \\
-Table 3: latency result on different kernel setups, in \textmu s\\
+Table 3: latency result on idle setup, in \textmu s\\
+\vspace{4mm} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{tabular}{|l|c|r|r|}
+\hline
+\multirow{2}{*}{} & \multicolumn{3}{c|}{user} \\ \cline{2-4} 
+ & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
+Xenomai 2 & 9.291 & 18.666 & 41.624 \\ \hline
+Xenomai 3 & 8.296 & 18.406 & 44.644 \\ \hline
+& \multicolumn{3}{c|}{kernel}       \\ \hline
+Xenomai 2 & 6.584 & 10.833 & 30.588 \\ \hline
+Xenomai 3 & 5.334 & 9.424 & 27.564  \\ \hline
+& \multicolumn{3}{c|}{timer-irq}    \\ \hline
+Xenomai 2 & 2.089 & 2.927 & 14.430  \\ \hline
+Xenomai 3 & 2.544 & 3.246 & 18.026  \\ \hline
+\end{tabular} \\
+\vspace{4mm} \\
+Table 4: latency result on cpu-stressed setup, in \textmu s\\
+\vspace{4mm} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-10-21 paper.tex
fix desc

--- 2015-10-21 paper.tex
@@
 While this is not an occasional case, we already ensured the same experiment method was ran a couple of times, we tried to look into the test code of latency to figure out the cause of this phenomenon.
-In user-level mode, the measurement task is carried out by the function 'latency' inside the program; whereas in kernel or irq mode, the task is executed by issuing a Xenomai RTDM command such as:
+In user-level mode, the measurement task is carried out by the function 'latency' inside the program; whereas in kernel or irq mode, the task is executed by issuing a Xenomai RTDM operation such as:
 \begin{verbatim}
@@
 However, comparing to Xenomai 2, our results show the unexpected slowdown of timer interrupt hanlding latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
-It is not clear why Cobalt in Xenomai 3 contributes to larger interrupt jitter measurement when the CPU is heavily loaded.
+It is not clear why Cobalt in Xenomai 3 contributes to larger interrupt jitter when the CPU is heavily loaded.
 This needs further investigation.

### 2015-10-21 paper.tex
remove unused

@@
 As for mainline Linux, the max latency easily exceeds 1 ms.
-When comparing the performance of Xenomai 3 to Xenomai 2, we can see that the statistics in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.
+When comparing the performance between Xenomai 2 and Xenomai 3, we can see that the statistics in cyclictest and latency test would be slightly better, except for the case of timer-irq latency in stressed condition.
 
 \section{Conclusions}
-We have evaluated the performance of two approaches to make Linux being real-time: PREEMPT\_RT and Xenomai, diversely presented in the view of single kernel and dual-kernel configurations on single-core ARM Cortex-A8, along with general conclusions about when each kernel configuration.
+We have evaluated the performance of two approaches to make Linux being real-time: PREEMPT\_RT and Xenomai, diversely presented in the view of single kernel and dual-kernel configurations on single-core ARM Cortex-A8.
 As for the dual kernel configuration of Xenomai 3, latency is still significantly better, but PREEMPT\_RT shows closer performance at least for Linux kernel 3.14 stable release while it enables to run same application on different platforms and migrate existing POSIX application to Linux systems.
 
-The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
-For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2.
+The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
+For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2 in general.
 However, comparing to Xenomai 2, our results show the unexpected slowdown of timer interrupt hanlding latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.

### 2015-10-21 paper.tex
Add table 4

--- 2015-10-21 paper.tex
@@
 \vspace{4mm} \\
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
 From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 us) than on Xenomai-2(below 3 us).

### 2015-10-21 paper.tex
recover deleted descriptions

@@
 
-Four distinct Linux kernel configurations are used for the experiments, as summarized in table below. Kernel are patched using git merge first, and remaining conflicts are resolved manually.
+Both Xenomai 3 Coblat and Xenomai 2 are working on the same I-pipe software for consistency.
 
@@
 
-The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
+The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments.
 For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2.

### 2015-10-21 paper.tex

@@
 \vspace{4mm} \\
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
 From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 us) than on Xenomai-2(below 3 us).

### 2015-10-21 paper.tex
Use \tabin to properly insert tables
Tables can now be tagged and referenced,
and manual spacing and resizing is no longer needed.

@@
 \refstepcounter{tabcounter} \label{#2}
-\[ \makebox[#1mm][c]{#4} \]
+\[ \makebox[#1][c]{#4} \]
 %\vspace{0mm}
@@
 
+\tabin{\columnwidth}{table:config}{Different kernel configurations for the experiment}{
 \begin{tabular}{|l| p{3cm} |l|}
@@
 Xenomai 3  & ipipe-core-3.14.39-arm-9 + xenomai v3.0 (Oct 8, 2015) & \cite{p-ipipe} \cite{git-x3} \\ \hline
-\end{tabular}\\
-\vspace{4mm} \\
-Table 1: Different kernel configurations for the experiment\\
+\end{tabular}
+}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%
+\tabin{\columnwidth}{table:cyclic}{cyclictest result on different kernel setups, in \textmu s}{
 \begin{tabular}{|l|r|r|r|}
@@
 Xenomai 3 & 6 & 16 & 37 \\ \hline
-\end{tabular}\\
-\vspace{4mm} \\
-Table 2: cyclictest result on different kernel setups, in \textmu s\\
-\vspace{4mm} \\
+\end{tabular}
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%
+\tabin{\columnwidth}{table:latency-idle}{latency result on idle setup, in \textmu s}{
 \begin{tabular}{|l|c|r|r|}
@@
 Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
-\end{tabular} \\
-\vspace{4mm} \\
-Table 3: latency result on idle setup, in \textmu s\\
-\vspace{4mm} \\
+\end{tabular}
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%
+\tabin{\columnwidth}{table:latency-cpu}{latency result on cpu-stressed setup, in \textmu s}{
 \begin{tabular}{|l|c|r|r|}
@@
 Xenomai 3 & 2.544 & 3.246 & 18.026  \\ \hline
-\end{tabular} \\
-\vspace{4mm} \\
-Table 4: latency result on cpu-stressed setup, in \textmu s\\
-\vspace{4mm} \\
+\end{tabular}
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-21 paper.tex
Fix double label, add ref to table 1
revise the synatx

--- 2015-10-21 paper.tex
@@
 \begin{abstract}
-Xenomai 3 is the new architecture of the real-time framework running seamlessly side-by-side Linux as a dual-kernel system like Xenomai 2, or natively over mainline Linux kernels supplemented by the PREEMPT\_RT efforts to meet stricter response time requirements than standard kernel preemption would bring.
+Xenomai 3 is the new architecture of the Linux real-time framework that runs seamlessly side-by-side Linux as a dual-kernel system like Xenomai 2, or natively over mainline Linux kernels.
+The mainline Linux kernels in the latter condition can be supplemented by the PREEMPT\_RT efforts to meet stricter response time requirements than standard kernel preemption would bring.
 In this presentation, we will evaluate the performances of Xenomai 3 running with dual-kernel configuration and analyze the various benchmarks for ARM Cortex-A series.

### 2015-10-21 paper.tex
use consistent PREEMPT_RT

@@
 Mainline Linux & 39 & 43 & 1046  \\ \hline
-Preempt-RT & 16 & 21 & 52 \\ \hline
+PREEMPT\_RT & 16 & 21 & 52 \\ \hline
 Xenomai 2 & 8 & 9 & 41 \\ \hline
@@
 Mainline Linux & 39 & 52 & 1097 \\ \hline
-Preempt-RT & 18 & 25 & 62 \\ \hline
+PREEMPT\_RT & 18 & 25 & 62 \\ \hline
 Xenomai 2 & 8 & 19 & 45 \\ \hline

### 2015-10-21 paper.tex
mention AM335x SoC

@@
 \subsubsection{Hardware}
-\textit{BeagleBone Black}\cite{bbb} is selected as our major testing hardware platform powered by \textit{TI AM335x} \cite{am335x}, and it is an effective embedded platform, capable of running Linux and Xenomai (both 2 and 3), consisting of a single 1GHz ARM Cortex-A8 processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
+\textit{BeagleBone Black}\cite{bbb} is selected as our major testing hardware platform powered by \textit{TI AM335x} \cite{am335x} SoC, and it is an effective embedded platform, capable of running Linux and Xenomai (both 2 and 3), consisting of a single 1GHz ARM Cortex-A8 processor, a 512 MB memory, 32kB L1 caches and a 256kB L2 cache.
 

### 2015-10-21 paper.tex
eps is deprecated. always use pdflatex
use consistent xenomai 3
we need more insightful conclusion

@@
 \setlength{\parskip}{2mm}
-
-%% insert eps pictures
-%% use as \epsin{epsfile}{width_in_mm}{label}{caption}
-\usepackage{epsfig}
-\newcounter{figcounter}
-\def\epsin #1#2#3#4{
-\refstepcounter{figcounter} \label{#3}
-\[
-\mbox{
-  \epsfxsize=#2mm
-  \epsffile{#1.eps}
-}
-\]
-%\vspace{0mm}
-\begin{center}
-  \parbox{7cm}{{\bf FIGURE \arabic{figcounter}:}\quad {\it #4 } } \\
-\end{center}
-}
 
@@
 Xenomai 2 provides skins to emulate traditional RTOS, such as VxWorks and pSOS, and a number of projects have been migrated smoothly from one of the supported traditional RTOS to Xenomai.
-In order to use a similar approach to migrate traditional RTOS projects to native Linux as well, Xenomai 3.x was launched.
+In order to use a similar approach to migrate traditional RTOS projects to native Linux as well, Xenomai 3 was launched.
 Thus, the single kernel configuration, Mercury, in Xenomai 3 does rely on the real-time capabilities of the native Linux kernel.
@@
 However, comparing to Xenomai 2, our results show the unexpected slowdown of timer-irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though.
-From our performance evaluation, Xenomai 3 is known as the most flexible real-time option.
 
